Specialisation \& the Latitude-niche-breadth Hypothesis

### 2015-10-09 talk/ABC_2015.tex
Now talk is done through results. Need to punch up the figures though.

      \vspace{.25cm}
      {\color{white}Fewer links per species\\in the tropics}

@@

      \vspace{.25cm}
      {\color{white}Equal links per species\\at all latitudes}

@@

      \vspace{.25cm}
      Fewer links per species\\in the tropics

@@

      \vspace{.25cm}
      Equal links per species\\at all latitudes

@@

    195 food webs \\
    0-78$^\circ$ (absolute latitude) \\
    Mean L/S, Generality, Vulnerability

@@

    195 food webs \\
    0-78$^\circ$ (absolute latitude) \\
    Mean \textbf{L/S}, Generality, Vulnerability

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/ls_vs_lat_simulated.eps}
    \end{center}

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

@@

  \begin{frame}{Does latitude affect LS vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $B \approx aS^{\color{purple}b}$

@@

  \begin{frame}{Does latitude affect LS vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $B \approx aS^{\color{purple}b_0+b_1Latitude}$

@@

  \begin{frame}{Does latitude affect LS vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $B \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$

@@

\section*{Results}
  \begin{frame}{Does latitude affect LS vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/marginals.eps}

      I want: just LS, maybe 2 columns?
      Maybe focus on Gen instead of LS? Easier to argue?

>>>>

      \vspace{.25cm}
      {\color{white}Fewer prey per species\\in the tropics}

@@

      \vspace{.25cm}
      {\color{white}Equal prey per species\\at all latitudes}

@@

      \vspace{.25cm}
      Fewer prey per species\\in the tropics

@@

      \vspace{.25cm}
      Equal prey per species\\at all latitudes

@@

    195 food webs \\
    0-78$^\circ$ (absolute latitude) \\
    {\color{white} Mean generality (\textbf{G})}

@@

    195 food webs \\
    0-78$^\circ$ (absolute latitude) \\
    Mean generality (\textbf{G})

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_lat_simulated.eps}

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}

@@

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $G \approx aS^{\color{purple}b}$

@@

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $G \approx aS^{\color{purple}b_0+b_1Latitude}$

@@

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$

@@

\section*{Results}
  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal_axis.eps}

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal_one.eps}

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal.eps}

\section*{Discussion}
